Super awesome embeddings

### 2019-02-03 paper/main.tex
Fill discussion for first two experiments

\begin{document}
\maketitle
\begin{abstract}
Abstract
\keywords{word sense disambiguation, word embeddings}

\end{abstract}

@@

\section{Experiments}
\subsection{Assumptions}
Since our goal is to check how embedding approach works for WSD problem, we use pretrained embedding model from spaCy - en\_vectors\_web\_lg.
Due to high impact of training data order on test results, as a result we take average score of 30 runs for each optimization.
\subsection{Baseline}
First of experiments is to check how out-of-the-box model works without extra optimizations. We perform tests with different context lengths, as a score we choose top 1 and top 3 accuracy. Results are shown in the Fig. \ref{fig:baseline}.

\begin{figure}
    \label{fig:baseline}
    \caption{Top accuracy of base model with different context length}
    \includegraphics[scale=0.5]{res/baseline_context_top_acc.png}
\end{figure}
TODO: Some discussion.
\subsection{Context length optimization}
Once we have base model results we check how simple alpha optimization improves accuracy based on context length. To do this, we choose arbitrarily a value for alpha parameter and run tests after one epoch of training the model. Since we average results from 30 runs we mark the measurement uncertainty on the graph. Results are shown in the Fig. \ref{fig:exp1}.
\begin{figure}
    \label{fig:exp1}
    \caption{Comparison of the base model and a little bit optimized model based on different context length}
    \includegraphics[scale=0.6]{res/exp1_context_top_acc.png}
\end{figure}
TODO: Some discussion.

@@

\begin{figure}
    \label{fig:exp2}
    \caption{Based on fixed context length, comparison of the base model and a model optimized with various alpha parameters. }
    \includegraphics[scale=0.6]{res/exp2_alpha_top_acc.png}
\end{figure}
TODO: Some discussion.
\subsection{Beta parameter optimization}
Next optimization we test is the influence of beta parameter. In this test we also performs one epoch of training with fixed context length and alpha parameter, based on previous experiment's results. Results are shown in the Fig. \ref{fig:exp3}. Since in this case we compare our solution to non-fully deterministic solution we decide to mark only averaged score of performed tests.

>>>>

\begin{document}
\maketitle
\begin{abstract}

In recent years word embeddings have been shown to boost the performance in NLP tasks such as syntactic parsing or sentiment analysis, but also in multimodal systems like image captioning or visual question answering.
It is therefore not surprising that word embeddings have been applied to Word Sense Disambiguation (WSD) problem as well.
In this work, we present how a simple word embeddings average-based method can be used to produce keyword (meaning) and context embeddings, and how the former can be improved with two embeddings distance optimization techniques.
We also open source the dataset that was created for the purpose of this research.
It is composed of 6 ambiguous words, with 4 to 7 meanings each, and collected real-world usage examples of those meanings, with tagged words to be disambiguated.

\keywords{word sense disambiguation, word embeddings}
\end{abstract}

@@

\section{Experiments}
\subsection{Assumptions}
Since our goal is to check how embedding approach works for WSD problem, we use pretrained embedding model from spaCy - en\_vectors\_web\_lg.
Due to high impact of training data order on test results, as a result we take average score of 30 runs for each optimization with random order of training data.
\subsection{Baseline}
First of experiments is to check how out-of-the-box model works without extra optimizations. We perform tests with different context lengths, as a score we choose top 1 and top 3 accuracy. Results are shown in the Fig. \ref{fig:baseline}.

\begin{figure}
    \label{fig:baseline}
    \caption{Top accuracy of base model with different context length}
    \includegraphics[scale=0.5]{res/baseline_context_top_acc.png}
\end{figure}

We see that the base model exceeds 90 percentages of top 3 accuracy for very short context length. It may be caused by low number of meanings of each disambiguation word.
We also see that top 1 score is the best for context length of 3 and we will use it in next two experiments as a baseline.

\subsection{Context length optimization}
Once we have base model results we check how simple alpha optimization improves accuracy based on context length. To do this, we choose arbitrarily a value for alpha parameter and run tests after one epoch of training the model. Since we average results from 30 runs we mark the measurement uncertainty on the graph. Results are shown in the Fig. \ref{fig:exp1}.
\begin{figure}
    \label{fig:exp1}
    \caption{Comparison of the base model and a little bit optimized model based on different context length}
    \includegraphics[scale=0.6]{res/exp1_context_top_acc.png}
\end{figure}
Independent on some noise caused by random order of training data, the optimized model is much better than the base model. Another fact is that for tested alpha parameter, longer context gives better results than with context's length obtained in the previous experiment.

@@

\begin{figure}
    \label{fig:exp2}
    \caption{Based on fixed context length, comparison of the base model and a model optimized with various alpha parameters. }
    \includegraphics[scale=0.6]{res/exp2_alpha_top_acc.png}
\end{figure}

We observe that optimal value of alpha is 0.25 but higher values may cause worse accuracy score than the baseline. As alpha is responsible for reducing distance between context and keyword (Equation \ref{eq:alpha_optimization}) and it is a scalar value, it may move the keyword to the other side and in the result the distance may be increased. It is one of things that can be improved in future work.

\subsection{Beta parameter optimization}
Next optimization we test is the influence of beta parameter. In this test we also performs one epoch of training with fixed context length and alpha parameter, based on previous experiment's results. Results are shown in the Fig. \ref{fig:exp3}. Since in this case we compare our solution to non-fully deterministic solution we decide to mark only averaged score of performed tests.
